Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-10 paper/paper.Rmd
Added dispersal to mean seed location

null_dispersion %>% 
  mutate(model = "Null") %>% 
  bind_rows(indiv_dispersion %>% 
              mutate(model = "Individual")) %>% 
  bind_rows(fam_dispersion %>% 
              mutate(model = "Family")) -> all_disp_data

@@

plot_grid(dispersal_box, dispersion_box, nrow = 2)

>>>>

null_dispersion %>% 
  mutate(model = "Null") %>% 
  bind_rows(indiv_dispersion %>% 
              mutate(model = "Individual")) %>% 
  bind_rows(fam_dispersion %>% 
              mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data

all_disp_data %>% 
  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
  geom_boxplot() -> dispersal_xy_box

@@

plot_grid(dispersal_xy_box, dispersal_box, dispersion_box, nrow = 3)
